Blueprint for efficient nuclear spin characterization in color center

### 2023-08-24 article.tex
ok
a

is necessary for enlarging the quantum register and precise description of the electron spin dynamics. Traditionally, nuclear spin characterisation is done with Optically Detected Magnetic Resonance (ODMR) (ref to Phillip Neumann's works), however the spectroscopic resolution is limited to the $T_2^\ast$ of the electron spin. Hence, some sequence is needed to increase the resolution. People have used Hahn Echo sequence to refocus the electron spin and enhance the coherence time of the electron spin \cite{childress2006coherent}. But this method only works for defects with a specific nuclear spins configuration. Depending on the applied protocol for nuclear spins characterization, the number of accessible nuclear spin can increase. Electron Spin Echo Envelop Modulation (ESEEM) types of sequences allow us to access the highest number of nuclear spins since the spectroscopy resolution is limited to the longitudinal relaxation time ($T_1$) of the system (see fig. \ref{fig:1}). 
\begin{figure*}%[htbp]
	\begin{center}
		\includegraphics[width=0.9\textwidth]{pict/drawing0.pdf}
		\caption{Comparing DD and 5pESEEM as two nuclear spin characterization method in different systems. a. An electron spin one system: in DD signal, each nuclear spin has a distinct resonance time up to first order of $A_{zz}$; the accuracy of the obtained hyperfine interaction is limited to $T_2$ of the electron spin. In the Fourier transform of the ESEEM signal, the two resonance frequency of each spin is present; the accuracy of the obtained hyperfine interaction is limited to $T_1$ of the electron spin b. An electron spin one system with two strongly coupled nuclear spins and many weakly coupled spins. No resonance time is detectable since the required condition for DD ($\omega_L \gg A_{zz}, A{zx}$) does not hold. However, resonant frequencies is still obtainable in the ESEEM signal c. An electron spin one half system: nuclear spins have more or less the same resonance time as it depends on the second order of hyperfine coupling. However, resonant frequency of each spins is distinguishable in the ESEEM signal. d. A system containing two different nuclear spin species: two nuclear spin bath can interfere in the DD signal, which makes the signal analysis more challenging. However, the species can be inferred from ESEEM signal since spe cies have different Larmor frequencies.}
		\label{fig:1}
	\end{center}
\end{figure*}

@@

\begin{figure*}%[htbp]

@@

		\includegraphics[width=0.9\textwidth]{pict/dd_compare2.pdf}

@@

\end{figure*}

@@

We want to make a sequence that is limited by T1 instead of T2. The idea of 5-pulse ESEEM \cite{kasumaj20085} is that to create an entanglement (Hahn-echo) before the free evolution (Ramsey). In other words, change the initial density matrix for the Ramsey sequence from such that entanglement already exist in the electron polarization terms of the density matrix. Fig \ref{fig:seqs} shows the sequence, which can be interpreted as two Hahn Echos that are separated by a long free evolution $T\gg T_2^\ast$ such that the coherence of the electron spin vanishes. The analytical formula to this sequence is provided in the appendix \ref{app:5pESEEM}. During the free evolution time, each nuclear spins oscillates with either of two resonance frequencies obtained from eq. \ref{eq:H}.
\begin{figure*}[htbp]
	\begin{center}
		\includegraphics[width=0.9\textwidth]{pict/eseem_compare2.pdf}
		\caption{Simulated FFT of ESEEM signal with a zoom into weakly coupled nuclear spins for the register reported \cite{abobeih2019atomic} assuming the electron spin is one-half. b. Enhancing the sensitivity to weakly coupled spins by increasing number of $\pi$-pulses to $N=72$ pulses in each entangling period. $\tau$ is set to the Larmor bright spot. Simulated Fisher information for the case of the electron spin c. one d. one-half system.}
		\label{fig:4}
	\end{center}
\end{figure*}
Fig \ref{fig:4} shows the furrier transform of the signal. Zooming into area close to the Larmor frequency reveals the weakly coupled nuclei. Each nuclear spins have two peaks in the spectrum. Expanding the resonance frequencies up to first order with respect to hyperfine coupling results that the weakly coupled nuclei keep their order as they go further away from the nuclei. This fact makes their characterization rather straight forward. To observe the weakly coupled nuclei more pronouncedly, one can use DDESEEM sequence by adding more $\pi$ pulses in the entangling periods. To distinguish other nuclei, extra measurements is required. One method is to use two dimensional hyperfine correlation spectroscopy (2D Hyscore)  \cite{vorobyov2022addressing}. However, this method is rather time-consuming as two time variables has to be swept. We suggest sweeping $\tau$ parameter and keep the track of frequency amplitude as a function of $\tau$. Two frequencies that belong to the same nuclear are correlated because the modulation depth oscillates with blind spot terms of both frequencies $\sin^2(\frac{\omega_0 \tau}{2}) \sin^2(\frac{\omega_1 \tau}{2})$. Fig. \ref{fig:5} shows two frequencies goes to bright and blind spots simultaneously. Hence, taking two dimensional correlation of the spectrum, one can deduce which two frequencies are correlated and belong to the same nuclear. \\

>>>>

is necessary for enlarging the quantum register and precise description of the electron spin dynamics. Traditionally, nuclear spin characterisation is done with Optically Detected Magnetic Resonance (ODMR) (ref to Phillip Neumann's works), however the spectroscopic resolution is limited to the $T_2^\ast$ of the electron spin. Hence, some sequence is needed to increase the resolution. People have used Hahn Echo sequence to refocus the electron spin and enhance the coherence time of the electron spin \cite{childress2006coherent}. But this method only works for defects with a specific nuclear spins configuration. Depending on the applied protocol for nuclear spins characterization, the number of accessible nuclear spin can increase. Electron Spin Echo Envelop Modulation (ESEEM) types of sequences allow us to access the highest number of nuclear spins since the spectroscopy resolution is limited to the longitudinal relaxation time ($T_1$) of the system (see fig. \ref{fig:1}). 
\begin{figure*}%[htbp]
	\begin{center}
		\includegraphics[width=0.9\textwidth]{pict/drawing0.pdf}
		\caption{Comparing DD and 5pESEEM as two nuclear spin characterization method in different systems. a. An electron spin one system: in DD signal, each nuclear spin has a distinct resonance time up to first order of $A_{zz}$; the accuracy of the obtained hyperfine interaction is limited to $T_2$ of the electron spin. In the Fourier transform of the ESEEM signal, the two resonance frequency of each spin is present; the accuracy of the obtained hyperfine interaction is limited to $T_1$ of the electron spin b. An electron spin one system with two strongly coupled nuclear spins and many weakly coupled spins. No resonance time is detectable since the required condition for DD ($\omega_L \gg A_{zz}, A{zx}$) does not hold. However, resonant frequencies is still obtainable in the ESEEM signal c. An electron spin one half system: nuclear spins have more or less the same resonance time as it depends on the second order of hyperfine coupling. However, resonant frequency of each spins is distinguishable in the ESEEM signal. d. A system containing two different nuclear spin species: two nuclear spin bath can interfere in the DD signal, which makes the signal analysis more challenging. However, the species can be inferred from ESEEM signal since species have different Larmor frequencies.}
		\label{fig:1}
	\end{center}
\end{figure*}

@@

\begin{figure}%[htbp]

@@

		\includegraphics[width=0.9\columnwidth]{pict/dd_compare2.pdf}

@@

\end{figure}

@@

We want to make a sequence that is limited by T1 instead of T2. The idea of 5-pulse ESEEM \cite{kasumaj20085} is that to create an entanglement (Hahn-echo) before the free evolution (Ramsey). In other words, change the initial density matrix for the Ramsey sequence from such that entanglement already exist in the electron polarization terms of the density matrix. Fig \ref{fig:seqs} shows the sequence, which can be interpreted as two Hahn Echos that are separated by a long free evolution $T\gg T_2^\ast$ such that the coherence of the electron spin vanishes. The analytical formula to this sequence is provided in the appendix \ref{app:5pESEEM}. During the free evolution time, each nuclear spins oscillates with either of two resonance frequencies obtained from eq. \ref{eq:H}.

\begin{figure*}[htbp]
	\begin{center}
		\includegraphics[width=0.9\textwidth]{pict/eseem_compare2.pdf}
		\caption{Simulated FFT of ESEEM signal with a zoom into weakly coupled nuclear spins for the register reported \cite{abobeih2019atomic} assuming the electron spin is one-half. b. Enhancing the sensitivity to weakly coupled spins by increasing number of $\pi$-pulses to $N=72$ pulses in each entangling period. $\tau$ is set to the Larmor bright spot. Simulated Fisher information for the case of the electron spin c. one d. one-half system.}
		\label{fig:4}
	\end{center}
\end{figure*}

>>>>>>> c0eaca02ca59681a3dedd48a17843824ce2f8aac
Fig \ref{fig:4} shows the furrier transform of the signal. Zooming into area close to the Larmor frequency reveals the weakly coupled nuclei. Each nuclear spins have two peaks in the spectrum. Expanding the resonance frequencies up to first order with respect to hyperfine coupling results that the weakly coupled nuclei keep their order as they go further away from the nuclei. This fact makes their characterization rather straight forward. To observe the weakly coupled nuclei more pronouncedly, one can use DDESEEM sequence by adding more $\pi$ pulses in the entangling periods. To distinguish other nuclei, extra measurements is required. One method is to use two dimensional hyperfine correlation spectroscopy (2D Hyscore)  \cite{vorobyov2022addressing}. However, this method is rather time-consuming as two time variables has to be swept. We suggest sweeping $\tau$ parameter and keep the track of frequency amplitude as a function of $\tau$. Two frequencies that belong to the same nuclear are correlated because the modulation depth oscillates with blind spot terms of both frequencies $\sin^2(\frac{\omega_0 \tau}{2}) \sin^2(\frac{\omega_1 \tau}{2})$. Fig. \ref{fig:5} shows two frequencies goes to bright and blind spots simultaneously. Hence, taking two dimensional correlation of the spectrum, one can deduce which two frequencies are correlated and belong to the same nuclear. \\
